---
title: "KCP(Kernel Change Point) permutation test"
author: "22058"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{KCP(Kernel Change Point) permutation test}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp22058__ is a R package developed to test the presence of correlation changes in a multivariate time series using KCP(Kernel Change Point) permutation method. 

There are two main test functions to implement the KCP permutation method, namely, _VarKCP_(Variance Test) and _Vardrop_(Variance drop test). In addition, the implementation of the two main functions needs to call other functions such as _Vexpression_ for which, both R and Rcpp versions are produced to compare the two versions' computation time and improve the running speed of the main test functions. Namely _VexpressionR_ for R and _VexpressionC_ for C++.

The R package 'microbenchmark' can be used to benchmark the above R and C++ functions.

## Functions in the R package

* __bandwidthC__ is a Function to compute the bandwidth using Rcpp. The function contains two loops, which could be slow with pure R language, especially when massive data is involved. Using the corresponding C++ code to improve the running speed.

```{r,eval=FALSE}
# Sort function
NumericVector SortC(NumericVector x){
  x.sort();
  return x;
}
# Median function
double medianC(NumericVector A){
  NumericVector B = SortC(A);
  int n = B.size();
  double m;
  if(n%2 != 0){
    m = B[n/2];
  }else{
    m = (B[n/2]+B[n/2-1])/2.0;
  }
  return m;
}

double bandwidthC(NumericMatrix X,int n){
  NumericVector d(n*(n-1)/2);
  int k = 0;
  for(int i=0; i<(n-1); i++){
    for(int j=i+1; j<n; j++){
      d[k] = sum((X(i,_)-X(j,_))*(X(i,_)-X(j,_)));
      k++;
    }
  }
  return medianC(d);
}
```

* __CorrelationR__ is a function to compute the running correlations in a multivariate time series. 
```{r,eval=FALSE}
CorrelationR <- function(X,N,v,w){
  n <- N-w
  Xcor <- matrix(0,n,v*(v-1)/2)
  for(i in 1:n){
    Xcorpart <- cor(X[i:(i+w),])
    l <- 1
    for(j in 1:(v-1)){
      for(k in (j+1):v){
        Xcor[i,l] = Xcorpart[j,k]
        l <- l+1
      }
    }
  }
  return(Xcor)
}
```

* __Vexpression__ is a function to compute the within-phase scatter. The source R code for _VexpressionR_ is as follows:
```{r,eval=FALSE}
VexpressionR <- function(X,n,a,b){
  s <- 0
  h2 <- bandwidthC(X,n)
  for(i in (a+1):(b-1)){
    for(j in (i+1):b){
      s <- s + 2*exp(-sum((X[i,]-X[j,])^2)/(2*h2))
    }
  }
  return((b-a-1)-s/(b-a))
}
```

* The source C++ code for _VexpressionC_ is as follows:
```{r,eval=FALSE}
double VexpressionC(NumericMatrix X,int n,double a,double b){
  double s = 0;
  double h2 = bandwidthC(X,n);
  for(int i=a; i<(b-1); i++){
    for(int j=i+1; j<b; j++){
      s = s + 2*exp(-sum((X(i,_)-X(j,_))*(X(i,_)-X(j,_)))/(2*h2));
    }
  }
  return (b-a-1)-s/(b-a);
}
```

* __VarKCP__ is a function to implement the variance test.
```{r,eval=FALSE}
VarKCP <- function(X,N,v,w){
  # compute the running correlations for raw data
  Xcor <- CorrelationR(X,N,v,w)
  # the number of time points in Xcor
  n <- N-w
  # the original statistic
  Var0 <- VexpressionC(Xcor,n,0,n)/n 
  
  R <- 999 # the number of permutation
  Var1 <- numeric(R)
  for (i in 1:R){
    n1 <- sample(1:N, size=N, replace = FALSE)
    X1 <- X[n1,]
    X1cor <- CorrelationR(X1,N,v,w)
    # The permutation statistic
    Var1[i] <- VexpressionC(X1cor,n,0,n)/n
  }
  # The significance level of permutation
  p <- mean(c(Var0,Var1)>Var0)
  return(p)
}
```

* __Vardrop__ is a function to implement the variance drop test.
```{r,eval=FALSE}
# The average within-phase variance
Rexpression <- function(Cpoint,X,n,K){
  V <- numeric(K+1) # K+1 is the number of phases
  V[1] <- VexpressionC(X,n,0,Cpoint[1])
  V[K+1] <- VexpressionC(X,n,Cpoint[K],n)
  if(K>1){
    for(i in 2:K){
      V[i] <- VexpressionC(X,n,Cpoint[i-1],Cpoint[i])
    }
  }
  return(sum(V)/n)
}
# Minimize the average within-phase variance
Min_Rexpr <- function(X,n,K){
  Initial <- runif(K,1,n)
  Lower <- numeric(K)+1
  Upper <- numeric(K)+n
  result <- solnp(par=Initial, fun=Rexpression,
                  LB=Lower, UB=Upper,
                  X=X, n=n, K=K)$values
  return(result[length(result)])
}
# The maximum drop in the minimum of the average within-phase variance
Max_Rmindrop <- function(X,n,K){
  Rmins <- Rmindrop <- numeric(K)
  for(i in 1:K){
    Rmins[i] <- Min_Rexpr(X,n,K)
  }
  Rmin0 <- VexpressionC(X,n,0,n)/n
  Rmin <- c(Rmin0,Rmins)
  for(i in 1:K){
    Rmindrop[i] <- Rmin[i+1]-Rmin[i]
  }
  return(max(Rmindrop))
}

Vardrop <- function(X,N,v,w,K){
  # compute the running correlations for raw data
  Xcor <- CorrelationR(X,N,v,w)
  # the number of time points in Xcor
  n <- N-w
  # the original statistic
  Rmindrop0 <- Max_Rmindrop(Xcor,n,K)
  
  R <- 10 # the number of permutation
  Rmindrops <- numeric(R)
  for (i in 1:R) {
    n1 <- sample(1:N, size=N, replace=FALSE)
    X1 <- X[n1,]
    X1cor <- CorrelationR(X1,N,v,w)
    # The permutation statistic
    Rmindrops[i] <- Max_Rmindrop(X1cor,n,K)
  }
  # The significance level of permutation
  p <- mean(c(Rmindrop0,Rmindrops)>Rmindrop0)
}
```

In order to empirically benchmark _VexpressionR_ and _VexpressionC_, one generates a time series with three variables drawn from a multivariate normal distribution with zero means and unit variance which contains __two correlation change points__, and save it in data{StatComp22058}. To load the file, one simply calls _data(mydata)_. 

## Benchmarking _VexpressionR_ and _VexpressionC_

The R code for benchmarking _VexpressionR_ and _VexpressionC_ is as follows.

```{r,eval=TRUE}
library(StatComp22058)
library(microbenchmark)
data(mydata)

N <- length(mydata[,1])# The number of time points
v <- length(mydata[1,])# The number of variables
w <- 15 # Set the width of windows for running correlation computation is 15
cordata <- CorrelationR(mydata,N,v,w)
n <- length(cordata[,1])

tm2 <- microbenchmark(
  VR = VexpressionR(cordata,n,0,n),
  VC = VexpressionC(cordata,n,0,n)
)
knitr::kable(summary(tm2)[,c(1,3,5,6)])
```

The results show an evident computational speed gain of C++ against R.

## KCP permutation test

The result of KCP permutation test is to look at the results of both the variance test and the variance drop test. Since there can be settings where one test can be more sensitive than the other, the KCP permutation test declares a significant correlation change in the data whenever at least one of them is significant.

## Variance test

```{r,eval=TRUE}
p_VarKCP <- VarKCP(mydata,N,v,w)
p_VarKCP
```

According to the result, the p value(0.001) of variance test is so small that we can reject the null hypothesis that there is no correlation change point. Therefore, a significant correlation change can be declared, which is consistent with reality.

## Variance drop test

```{r,eval=FALSE}
library(Rsolnp)
p_Vardrop <- Vardrop(mydata,N,v,w,2)
p_Vardrop
```

The variance test and the variance drop test can't determine the true number of change points, but only reveals that the time series contains at least one correlation change.

